A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-26 paper/elsarticle/elsarticle-template.tex
paper

Calibrating a camera can be carried out by relying on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is used to obtain the maximum likelihood estimate of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations $(\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the cumulative reprojection error
\begin{equation}
\sum_{i=0}^{n_\text{pt}} \sum_{j=0}^{n_\text{im}} d_\omega\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j}' = \mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j \in \mathbb{R}^3$ expresses $\mathbf{X}_{i,j}$ in the camera coordinate frame of the camera corresponding to the $j^{\text{th}}$ calibration image, $(\mathbf{x}_{i,j}', 1)^\top \sim \mathtt{K}\mathbf{X}_{i,j}' \in \mathbb{P}^2$ gives the projection~$\mathbf{x}'_{i,j} \in \mathbb{R}^2$ of $\mathbf{X}_{i,j}'$ to that image, and $d_\omega$ is a distance function that~(i) corrects for lens distortion using the lens distortion model coefficients~$\omega$ \cite{duane1971close,weng1992camera} and (ii) returns a distance with respect to the two undistorted pixel positions. The inverse rigid body transformation~$(\mathtt{R}_j^{-1}, -\mathtt{R}_j^{-1}\mathbf{t}_j^{})$ gives the pose of the $j^{\text{th}}$~camera relative to the 3D points of the calibration pattern.

>>>>

Calibrating a camera can be carried out by relying on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output maximum likelihood estimates of the camera calibration matrix, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. Images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is then used to obtain the maximum likelihood estimates~$(\hat{\omega}, \hat{\mathtt{K}}, \{(\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)\})$ of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations $(\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the cumulative reprojection error
\begin{equation}
%\sum_{i=0}^{n_\text{pt}} \sum_{j=0}^{n_\text{im}} d_\omega\big(\mathbf{x}_{i,j}, \pi_{\mathtt{K},\mathtt{R}_j,\mathbf{t}_j}(\mathbf{X}_{i,j})\big),
\sum_{i=0}^{n_\text{pt}} \sum_{j=0}^{n_\text{im}} d_{\hat{\omega}}(\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'),
\label{re}
\end{equation}
where $\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j \in \mathbb{R}^3$ expresses $\mathbf{X}_{i,j}$ in the camera coordinate frame of the camera corresponding to the $j^{\text{th}}$~calibration image and $(\hat{\mathbf{x}}_{i,j}'^\top, 1)^\top \sim \hat{\mathtt{K}}(\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j) \in \mathbb{P}^2$ gives the projection~$\hat{\mathbf{x}}_{i,j}' \in \mathbb{R}^2$ of the point~$\mathbf{X}_{i,j}$ to the that image. The function~$d_\omega$ is a distance function that computes a distance with respect to the two pixel positions corrected for lens distortions, in accordance with the lens distortion model coefficients~$\hat{\omega}$ \cite{duane1971close,weng1992camera}. The inverse rigid body transformation~$(\hat{\mathtt{R}}_j^{-1}, -\hat{\mathtt{R}}_j^{-1}\hat{\mathbf{t}}_j^{})$ gives the pose of the $j^{\text{th}}$~camera relative to the 3D points of the calibration pattern.
